Transcriptomic Analysis for Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-07-05 Cover_letter_JPM.tex
Updates from Overleaf

% modify on main.tex, marked with
%\begin{MyColorPar}{red}
%\end{MyColorPar}
% from page (ok)
% Please see page 3, line 23. begins on line 1, page 3, to line 2, page 4.
The summary of holistic cancer care in this revised manuscript could be on the paragraphs marked in \textcolor{red}{Red} on page 13 (line 377 to 392).
%and on page \pageref{from:answer1-2}, line?
%\lr{to:answer1-2}. \lineref[1]{to:answer1-2}),
% \lr{from:answer1-2}
%(line 377 \ref{line_fr:answer1-2}) to page \pageref{page_to:answer1-2} (line 392 \ref{line_to:answer1-2}). 
%\pagelabel{from:answer1-2} \linelabel{from:answer1-2L}
Also, it is shown here in the following paragraph.
% line \ref{line_fr:answer1-2} ~ \ref{line_to:answer1-2} of page %\pageref{page_fr:answer1-2}, \pageref{page_to:answer1-2}
% in main.tex
% %\label{page_fr:answer1-2}, \label{page_to:answer1-2}
% \linelabel{line_fr:answer1-2} , \linelabel{line_to:answer1-2}

\begin{MyIndent}
\begin{MyColorPar}{red}
" %discussion: the third limitation
There are 81 physical, pathological and social conditions derived from participants available for survival modeling in the TCGA, % since it has comprehensive clinical features, 
such as age, gender, residual tumor, vital status, days-to-last-followup, cancer stage, smoking duration, exposure to alcohol, asbestos, radioactive radon. 
However, the TCGA did not collect other features related to holistic care.
% Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage; emotional 情緒(心)
Going for holistic cancer care\cite{Mehta2019}\cite{Iftikhar2021}, spiritual and emotional condition is equally essential comparing with physical and social status (see Figure 5).%\ref{fig:figure5}).
Psychosocial stress is associated with cancer incidence\cite{Lutgendorf2010}\cite{Powell2013}\cite{Iftikhar2021}, metastasis\cite{Lutgendorf2010}\cite{Moreno-Smith2010}\cite{Du2020}\cite{Xu2021}, and poor survival\cite{Chida2008}.
These impacts might be mediated through the hypothalamic-pituitary-adrenal (HPA) axis\cite{Hsiao2012}.
Holistic healthcare providers will engage his/her patients with eye-to-eye contact in terms of mind-to-mind connection. Their empathy, sympathy, and compassion are induced by the suffering of patients from those diseases. They will try to treat patients by prescribing medicine (and "themselves") or performing surgery.
Thus, the healing resilience of patients will be induced by unconditional positive regard. % of healing.
The patients will trust those who take care of them and have the confidence to increase the capacity to recover from diseases through a mind-brain-body connection manner (see Figure 5).%\ref{fig:figure5}).
"
\end{MyColorPar} %red
\end{MyIndent}
%身心靈全人醫療，展現魅力、慈悲心，靈性成熟的醫師，用藥物或手術來治療病患時，「他自己本身」就具有療癒效果
%「把自己當藥方開出去」

@@

%There is so many thing we could find during the data mining from so many 20500 protein-coding genes.
We performed the FDR correction applied on the Kaplan-Meier \textit{P} values of cutoff finding procedure, then Bonferroni adjustment of those \textit{P} values for candidate selection.
%\begin{MyColorPar}{red}
%\end{MyColorPar}
% and FDR (done; ok)
We modified Figure 5 (with three candidates) and the last paragraph of "Cutoff Finder Core Engine" in the Materials and Methods section.
%Figure 1, Table 1, 2 correction: Kaplan-Meier FDR correction
%***The caption of Figure 1 and Table 1 has description about 1) FDR correction of Kaplan-Meier \textit{P} values during Cutoff finding; and 2) Bonferroni correction of Kaplan-Meier \textit{P} values after Cox modeling for candidate selection.
The paragraphs marked in \textcolor{red}{Red} from page 16 (line 502 to line 505) are the part of the manuscript that has been revised. Also, it is shown here in the following paragraph.
\\[0.3cm]

@@

We modified the paragraphs in the "Materials and Methods" section, and "Results" section for the analysis of GSE65858.
We also described "the \textit{P} values are affected by the sample size" in the "Discussions" section.
% ok
The paragraphs in "Materials and Methods" marked in \textcolor{red}{Red} on page 18 (line 560 to line 572),
% results ok
the paragraphs in "Results" marked in \textcolor{red}{Red} from page 5 (line 148) to page 6 (line 172) , and
% ok
the paragraphs in "Discussions" marked in \textcolor{red}{Red} from page 10 (line 236) to page 11 (line 280)
are the part of the manuscript that has been revised. 
Also, it is shown here in the following paragraph.
\\[0.3cm]

@@

We appreciate the reviewer for the critical comment and modified the Materials and Methods accordingly.
% ok
The paragraphs marked in \textcolor{red}{Red} on page 17 (line 518 to line 544) are the part of the manuscript that has been revised. Also, it is shown here in the following paragraph.
\\[0.3cm]

\begin{MyIndent}
\begin{MyColorPar}{red}
%The Cox proportional hazards regression is the widely accepted approach for modeling survival while 
"
The Cox proportional-hazards regression model\cite{Cox1972}\cite{Andersen1982} is commonly used for modeling survival analysis data. It allows analyzing survival for one or more predictor variables and to provides the effect size (coefficients) for them\cite{Bradburn2003b}. % Classification trees and artificial neural networks in survival analysis
The Cox model is also accounting for confounding factors\cite{Magen2019}.
It is expressed by the hazard function denoted by h(t). Briefly, the hazard function can be interpreted as the risk of a specific event (e.x., death) at time t. It can be estimated as follow:

@@

% 不要誇大說明 謙虛道歉
We apologize for exaggerating the difficulties of our workflow.
% ok
The paragraphs marked in \textcolor{red}{Red} on page 11 (line 282 to line 310) are the part of the manuscript that has been revised. Also, it is shown here in the following two paragraphs.

@@

According to the reviewer's comment, the Discussions was modified accordingly. The paragraphs marked in \textcolor{red}{Red} from page 11 (line 257) to page 13 (line 354) are the part of the manuscript that has been revised. Also, it is shown here in the following paragraph.
\\[0.3cm]
%(the revised portions in the manuscript are indicated in \textcolor{red}{red})

>>>>

% modify on main.tex, marked with
%\begin{MyColorPar}{red}
%\end{MyColorPar}
% from page (ok)
% Please see page 3, line 23. begins on line 1, page 3, to line 2, page 4.
The summary of holistic cancer care in this revised manuscript could be on the paragraphs marked in \textcolor{red}{Red} on page 13 (line 381) to page 14 (line 396).
%and on page \pageref{from:answer1-2}, line?
%\lr{to:answer1-2}. \lineref[1]{to:answer1-2}),
% \lr{from:answer1-2}
%(line 377 \ref{line_fr:answer1-2}) to page \pageref{page_to:answer1-2} (line 392 \ref{line_to:answer1-2}). 
%\pagelabel{from:answer1-2} \linelabel{from:answer1-2L}
Also, it is shown here in the following paragraph.
% line \ref{line_fr:answer1-2} ~ \ref{line_to:answer1-2} of page %\pageref{page_fr:answer1-2}, \pageref{page_to:answer1-2}
% in main.tex
% %\label{page_fr:answer1-2}, \label{page_to:answer1-2}
% \linelabel{line_fr:answer1-2} , \linelabel{line_to:answer1-2}

\begin{MyIndent}
\begin{MyColorPar}{red}
" %discussion: the third limitation
There are 81 physical, pathological and social conditions derived from participants available for survival modeling in the TCGA, % since it has comprehensive clinical features, 
such as age, gender, residual tumor, vital status, days-to-last-followup, cancer stage, smoking duration, exposure to alcohol, asbestos, radioactive radon. 
However, the TCGA did not collect other features related to holistic care.
% Input $X_1...X_n$ (e.x. patients features: such as age, gender, gene expression, cancer stage; emotional 情緒(心)
Going for holistic cancer care\cite{Mehta2019}\cite{Iftikhar2021}, spiritual and emotional condition is equally essential comparing with physical and social status (see Figure 6).%\ref{fig:figure5}).
Psychosocial stress is associated with cancer incidence\cite{Lutgendorf2010}\cite{Powell2013}\cite{Iftikhar2021}, metastasis\cite{Lutgendorf2010}\cite{Moreno-Smith2010}\cite{Du2020}\cite{Xu2021}, and poor survival\cite{Chida2008}.
These impacts might be mediated through the hypothalamic-pituitary-adrenal (HPA) axis\cite{Hsiao2012}.
Holistic healthcare providers will engage his/her patients with eye-to-eye contact in terms of mind-to-mind connection. Their empathy, sympathy, and compassion are induced by the suffering of patients from those diseases. They will try to treat patients by prescribing medicine (and "themselves") or performing surgery.
Thus, the healing resilience of patients will be induced by unconditional positive regard. % of healing.
The patients will trust those who take care of them and have the confidence to increase the capacity to recover from diseases through a mind-brain-body connection manner (see Figure 6).%\ref{fig:figure5}).
"
\end{MyColorPar} %red
\end{MyIndent}
%身心靈全人醫療，展現魅力、慈悲心，靈性成熟的醫師，用藥物或手術來治療病患時，「他自己本身」就具有療癒效果
%「把自己當藥方開出去」

@@

%There is so many thing we could find during the data mining from so many 20500 protein-coding genes.
We performed the FDR correction applied on the Kaplan-Meier \textit{P} values of cutoff finding procedure, then Bonferroni adjustment of those \textit{P} values for candidate selection.
%\begin{MyColorPar}{red}
%\end{MyColorPar}
% and FDR (done; ok)
We modified Figure 5 (with three candidates) and the last paragraph of "Cutoff Finder Core Engine" in the Materials and Methods section.
%Figure 1, Table 1, 2 correction: Kaplan-Meier FDR correction
%***The caption of Figure 1 and Table 1 has description about 1) FDR correction of Kaplan-Meier \textit{P} values during Cutoff finding; and 2) Bonferroni correction of Kaplan-Meier \textit{P} values after Cox modeling for candidate selection.
The paragraphs marked in \textcolor{red}{Red} from page 17 (line 505 to line 508) are the part of the manuscript that has been revised. Also, it is shown here in the following paragraph.
\\[0.3cm]

@@

We modified the paragraphs in the "Materials and Methods" section, and "Results" section for the analysis of GSE65858.
We also described "the \textit{P} values are affected by the sample size" in the "Discussions" section.
% ok
The paragraphs in "Materials and Methods" marked in \textcolor{red}{Red} on page 18 (line 567 to line 580),
% results ok
the paragraphs in "Results" marked in \textcolor{red}{Red} from page 5 (line 154) to page 6 (line 169) , and
% ok
the paragraphs in "Discussions" marked in \textcolor{red}{Red} from page 10 (line 233) to page 11 (line 284)
are the part of the manuscript that has been revised. 
Also, it is shown here in the following paragraph.
\\[0.3cm]

@@

We appreciate the reviewer for the critical comment and modified the Materials and Methods accordingly.
% ok
The paragraphs marked in \textcolor{red}{Red} on page 17 (line 521 to line 551) are the part of the manuscript that has been revised. Also, it is shown here in the following paragraph.
\\[0.3cm]

\begin{MyIndent}
\begin{MyColorPar}{red}
%The Cox proportional hazards regression is the widely accepted approach for modeling survival while 
"
The Cox proportional-hazards regression model\cite{Cox1972}\cite{Andersen1982} is commonly used for modeling survival data. It allows analyzing survival for one or more variables and to provides the effect size (coefficients, i.e., hazard ratios) for them\cite{Bradburn2003b}. % Classification trees and artificial neural networks in survival analysis
The Cox model is also accounting for confounding factors\cite{Magen2019}.
It is expressed by the hazard function denoted by h(t). Briefly, the hazard function can be interpreted as the risk of a specific event (e.x., death) at time t. It can be estimated as follow:

@@

% 不要誇大說明 謙虛道歉
We apologize for exaggerating the difficulties of our workflow.
% ok
The paragraphs marked in \textcolor{red}{Red} on page 11 (line 286) to page 12 (line 314) are the part of the manuscript that has been revised. Also, it is shown here in the following two paragraphs.

@@

According to the reviewer's comment, the Discussions was modified accordingly. The paragraphs marked in \textcolor{red}{Red} from page 11 (line 257) to page 13 (line ?) are the part of the manuscript that has been revised. Also, it is shown here in the following paragraph.
\\[0.3cm]
%(the revised portions in the manuscript are indicated in \textcolor{red}{red})
